---
title: "Class 4 solutions"
author: "Pernille Brams"
date: "22/2/2024"
output:
  html_document:
    toc: true  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs}
library(pacman)

pacman::p_load(tidyverse,
               ggpubr,
               rstanarm)

```

# By hand or Latex syntax in a .Rmd file
Most of these exercises are easiest solved by hand. However, if you want to write math notation in an R-markdown Latex-syntax can be used. Below are some examples of how latex is used to write math equations. Remember to surround your equation by either $ $ or $$ $$.

Example: 
$\frac{5}{10}$

$$
x^{\frac{a}{b}}=\left(x^a\right)^{\frac{1}{b}}=\left(x^{\frac{1}{b}}\right)^a=\sqrt[b]{x^a}
$$
# Exercises
[Uploading solutions in hand]
In the GILL book (in this order):
1.1 - made by hand
1.2 - made by hand
1.3 - made by hand
1.15 - made by hand
1.4 - made by hand
The rest from the lecture's last slide.

# Extra about Bayesian, if you finish early (extra = optional!)
## Ex. 1: Load rstanarm()
See above

## Ex. 2: Simulate data for a simple linear regression model, y = b0 + b1*X+e, where x is a predictor variable, y is the outcome, and e is the normally distributed error.
```{r}
#Defining variables
b0 <- 10
b1 <- 6.8
e <- rnorm(100, mean = 1, sd = 0.5)

x0 <- rnorm(100, mean = 5, sd = 2)
y0 <- b0 + b1*x0+e

df_2 <- data.frame(x0 = x0, y0 = y0, b0 = b0, b1 = b1, e = e)

```


## Ex. 3: Fit a Bayesian linear regression model using stan_glm from the rstanarm package with default priors.
```{r}
fit <- stan_glm(y0 ~ x0, data = df_2, chains = 1)
prior_summary(fit)
help('prior_summary.stanreg')
```


## Ex. 4: Explain in a few sentences what a prior is (this is difficult stuff, so light level here is totally fine)
I don't know what is going on.

## Ex. 5: Refit model using different priors for b0 and b1.


